Supplementary Figures

### 2024-04-19 02b_supplementary_plots.Rmd
add top mods

```{r}
horizon_skill <- 
  temperature_skill |> 
  filter(!(model_id %in% c(top_mods$model_id)), 
         horizon > 0, 
         horizon != 15,
         horizon <=30) |> 
  group_by(model_id, horizon) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  left_join(select(model_meta, model_id, manuscript_name)) |> 
  # mutate(manuscript_name = factor(manuscript_name, levels = levels(model_id_colours$manuscript_name))) |> 
  ggplot(aes(x=horizon, 
             y = mean_crps, colour = manuscript_name, linetype = manuscript_name)) +
  geom_hline(yintercept = 0, colour = 'grey40' ) + 
  geom_line(show.legend = F)  +  
  labs(y='Mean relative skill (°C)', x = 'Horizon (days)') +
  theme_bw()

>>>>

```{r}
top_mods <- temperature_skill |> 
  group_by(model_id) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  ungroup() |> 
  filter(mean_crps > 0) |> 
  distinct(model_id)

horizon_skill <- 
  temperature_skill |> 
  filter(!(model_id %in% c(top_mods$model_id)), 
         horizon > 0, 
         horizon != 15,
         horizon <=30) |> 
  group_by(model_id, horizon) |> 
  summarise(mean_crps = mean(skill_crps, na.rm = T)) |> 
  left_join(select(model_meta, model_id, manuscript_name)) |> 
  # mutate(manuscript_name = factor(manuscript_name, levels = levels(model_id_colours$manuscript_name))) |> 
  ggplot(aes(x=horizon, 
             y = mean_crps, colour = manuscript_name, linetype = manuscript_name)) +
  geom_hline(yintercept = 0, colour = 'grey40' ) + 
  geom_line(show.legend = F)  +  
  labs(y='Mean relative skill (°C)', x = 'Horizon (days)') +
  theme_bw()
